The expected shape of the Milky Way's Dark Matter halo

### 2019-02-05 Paper/paper.tex
tablas corregidas

\begin{table*}
\centering
\begin{tabular}{l|cc|cc|cc|cc}
\hline
\hline
Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
\multicolumn{2}{c}{$R_{vir}$/Kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ \hline
halo 6&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ \hline
halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ \hline
halo 16&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ \hline
halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ \hline
halo 21&4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ \hline
halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ \hline
halo 23&3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\\hline
halo 24&4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ \hline
halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
halo 26&4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\\hline
halo 27&5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ \hline
halo 28&4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
halo 29&4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
halo 30&3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
\hline
\hline
\end{tabular}
\caption{Specifications of each level 4 galaxy (halo). The DM and MHD versions of each parameters are presented together. The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
\label{tab:level4}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{l?cc?cc?cc?cc}
\hline
\hline
Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/Kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
\hline
\hline
\end{tabular}
\caption{Specifications of each level 3 galaxy (halo). The DM and MHD versions of each parameters are presented together. The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
\label{tab:level3}
\end{table*}

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is
  not clear. Some studies claim that the DM halo must be oblate, at
  least in the vicinities of the disk, to ensure its stability
  . However,)))} not much is said about its
dependence with radius as previous studies focus rather on the effects
of baryons on the dynamics of the halo at fixed radii. Examining the
representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
some things are noticeable: first, the DM halo is almost perfectly
oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

@@

This rounding effect is expected from the gravitational effect of the
flattened axisymmetric galactic disk. It is also reasonable that this
effect is not as strong at $\approx 100$Kpc, where the disk potential
is dimmer compared to the DM halo potential. Keeping this in mind, one
would expect that the rounding effect of baryons is related to some
galactic parameters such as its component masses and radii. However,
even for the parameter of highest correlation with this rounding
effect (the baryonic fraction), the relation is not clear nor
conclusive due to the dispersion from galaxy peculiarities. In figure
\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
baryonic fraction of each galaxy. Although some linear tendency is
suggested qualitatively, the dispersion of the sample is very high to
obtain some conclusive relation. This is an evidence that
adiabatic-contraction models are not realistic as they may neglect
some effects of the galaxy evolution in the whole cosmological
context.

@@

Although the effect of the baryonic disk on the shape of the DM halo
is a reasonable explanation for the rounding effect, it does not
actually explain the deviation from oblateness of MHD halos at
$r<10$Kpc. In other words, if the disk is perfectly axisymmetric,
there must be some source of triaxiality at $r<10$Kpc to explain the
low axial ratios.

>>>>

\begin{table*}
\centering
\begin{tabular}{l|cc|cc|cc|cc}
\hline
\hline
Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
\multicolumn{2}{c}{$R_{vir}$/kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ 
halo 6 ($\star$)&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ 
halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ 
halo 16 ($\star$)&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ 
halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ 
halo 21 ($\star$) &4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ 
halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ 
halo 23 ($\star$) &3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\
halo 24 ($\star$) &4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ 
halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
halo 26 &4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\
halo 27 ($\star$) & 5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ 
halo 28 & 4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
halo 29 & 4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
halo 30 & 3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
\hline
\hline
\end{tabular}
\caption{Specifications of each level 4 galaxy (halo). 
  The DM and MHD versions of each parameters are presented together. 
  The columns correspond to: (1) Halo name, (2,3) Millions of DM
  particles belonging to the halo, (4,5) DM particle mass in
  $10^5M_\odot$, (6,7) Halo Virial radius in kpc and (8,9) halo virial
  mass in $10^{14}M_\odot$. Halos marked with a star ($\star$) are
  correspond to halos resimulated at higher resolution (level 3).}  
\label{tab:level4}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{l?cc?cc?cc?cc}
\hline
\hline
Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
\hline
\hline
\end{tabular}
\caption{Same layout Table \ref{tab:level3} for Level 3 simulations (higher
  resolution than Level 4 simulations).}
\label{tab:level3}
\end{table*}

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is
  not clear. Some studies claim that the DM halo must be oblate, at
  least in the vicinities of the disk, to ensure its stability
  . However,)))} not much is said about its
dependence with radius as previous studies focus rather on the effects
of baryons on the dynamics of the halo at fixed radii. Examining the
representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
some things are noticeable: first, the DM halo is almost perfectly
oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

@@

This rounding effect is expected from the gravitational effect of the
flattened axisymmetric galactic disk. It is also reasonable that this
effect is not as strong at $\approx 100$kpc, where the disk potential
is dimmer compared to the DM halo potential. Keeping this in mind, one
would expect that the rounding effect of baryons is related to some
galactic parameters such as its component masses and radii. However,
even for the parameter of highest correlation with this rounding
effect (the baryonic fraction), the relation is not clear nor
conclusive due to the dispersion from galaxy peculiarities. In figure
\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
baryonic fraction of each galaxy. Although some linear tendency is
suggested qualitatively, the dispersion of the sample is very high to
obtain some conclusive relation. This is an evidence that
adiabatic-contraction models are not realistic as they may neglect
some effects of the galaxy evolution in the whole cosmological
context.

@@

Although the effect of the baryonic disk on the shape of the DM halo
is a reasonable explanation for the rounding effect, it does not
actually explain the deviation from oblateness of MHD halos at
$r<10$kpc. In other words, if the disk is perfectly axisymmetric,
there must be some source of triaxiality at $r<10$kpc to explain the
low axial ratios.
